Reproduction of Civic Honesty around the Globe

### 2021-03-24 outputs/paper/paper.Rmd
Update paper.Rmd

The selection of countries raises another issue of the dataset: Do those countries really represent the globe? 40 countries are selected and examined for the research, and almost half (19 countries) of them are European countries. However, in reality, the population of all European countries is approximately 10% of the world's population [@citeWorldContinents]. In terms of the number of countries, there are merely 44 countries in Europe, out of 195 countries in the world, which accounts for about one-fourth of the total countries [@citeCountriesEurope]. Is it because those unselected countries could not meet the requirements of selection criteria? The selection criteria requirements for the country category are as follows:

```{r, include = FALSE, message = FALSE}
dfPwr <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1)

```{r, echo = FALSE, message = FALSE}
freqByCond <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1) %>%
  group_by(cond, response) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

@@

```{r, echo = FALSE, message = FALSE}

@@

ggplot(dfRatings, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 2, 
                color = colorGray,
                colour_x = colorOrange, 
                colour_xend = colorRed,
                dot_guide = TRUE, 
                dot_guide_size = 0.05,
                show.legend = TRUE) +
                # TODO: Fix legend 
  labs(x = NULL, y = NULL, title = "Share of wallets reported by country") +
  theme_minimal() +
  scale_color_manual(name = "", values = c("red", "blue")) +
  theme(panel.grid.major.x = element_line(size = 0.02))

@@

>>>>

Figure \@ref(fig:figReportedByCountry) is a replica of a dumbbell plot included in the original research paper, which shows share of returned (reported) wallets in NoMoney and Money conditions by country. As can be seen in the figure, people were more likely to return wallets with more money in most of the countries selected for the research. If so, can we say that people tend to return wallets contained more money in "most countries"?

@@

```{r figReportedByCountry, echo = FALSE, message = FALSE, fig.cap="Share of wallets reported in the NoMoney and Money conditions, by country"}

@@

ggplot(dfRatings, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 2, 
                color = colorGray,
                colour_x = colorOrange, 
                colour_xend = colorRed,
                dot_guide = TRUE, 
                dot_guide_size = 0.05,
                show.legend = TRUE) +
                # TODO: Fix legend 
  labs(x = NULL, y = NULL, title = "") +
  theme_minimal() +
  scale_color_manual(name = "", values = c("red", "blue")) +
  theme(panel.grid.major.x = element_line(size = 0.02))

@@

The selection of countries raises another issue of the dataset: Do those chosen countries really represent the globe? 40 countries are selected and examined for the research, and almost half (19 countries) of them are European countries. However, in reality, the population of all European countries is approximately 10% of the world's population [@citeWorldContinents]. In terms of the number of countries, there are merely 44 countries in Europe, out of 195 countries in the world, which accounts for about one-fourth of the total countries [@citeCountriesEurope]. Is it because those unselected countries could not meet the requirements of selection criteria? The selection criteria requirements for the country category are as follows:

```{r, include = FALSE, message = FALSE}
### Cross Table for the control and treatment groups
dfPwr <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1)

```{r, echo = FALSE, message = FALSE}
### The result of the power analysis
freqByCond <-
  dfBehavModel %>%
  select('cond',
         'response') %>%
  filter(cond == 0 | cond == 1) %>%
  group_by(cond, response) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
